---
title: "Homework2 Submission1"
author: "Moyo Odugbemi"
subtitle: "https://github.com/modugbe/homework2"
format: 
   pdf: 
     df-print: default
     output-file: "odugbemi-m-hwk2-1"
     output-ext: "pdf"
     header-includes:
        - \usepackage{float}
        - \floatplacement{table}{H}
---

```{r results="hide", echo=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(lubridate)
# Load the HCRIS data
final.hcris.data <- read_rds("/Users/moyosoreoluwaodugbemi/Econ 470/Homework2/data/output/HCRIS_Data.rds")
```

\newpage
#Question 1
```{r results="hide", echo=FALSE, message=FALSE}
final.hcris.v1996=read_rds('/Users/moyosoreoluwaodugbemi/Econ 470/Homework2/data/output/HCRIS_Data_v1996.rds')
final.hcris.v2010=read_rds('/Users/moyosoreoluwaodugbemi/Econ 470/Homework2/data/output/HCRIS_Data_v2010.rds')

## create missing variables for columns introduced in v2010 of hcris forms
final.hcris.v1996 = final.hcris.v1996 %>%
  mutate(hvbp_payment=NA, hrrp_payment=NA)

## combine v1996 and v2010 hcris forms, and sort by provider_number/year
final.hcris=rbind(final.hcris.v1996,final.hcris.v2010) %>%
  mutate(fy_end=mdy(fy_end),fy_start=mdy(fy_start),
         date_processed=mdy(date_processed),date_created=mdy(date_created),
         tot_discounts=abs(tot_discounts), hrrp_payment=abs(hrrp_payment)) %>%
  mutate(fyear=year(fy_end)) %>%
  arrange(provider_number,fyear) %>%
  select(-year)

## count of hospitals/provider_number by year
final.hcris %>% group_by(fyear) %>% count()

# Clean data --------------------------------------------------------------

## create count of reports by hospital fiscal year
final.hcris =
  final.hcris %>% 
  add_count(provider_number, fyear, name="total_reports")

## create running total of reports
final.hcris =
  final.hcris %>% 
  group_by(provider_number, fyear) %>%
  mutate(report_number=row_number())

## identify hospitals with only one report per fiscal year 
## this will be the first set of hospitals in the final dataset
unique.hcris1 =
  final.hcris %>%
  filter(total_reports==1) %>%
  select(-report, -total_reports, -report_number, -npi, -status) %>%
  mutate(source='unique reports')


## identify hospitals with multiple reports per fiscal year
duplicate.hcris = 
  final.hcris %>%
  filter(total_reports>1) %>%
  mutate(time_diff=fy_end-fy_start)

library(ggplot2)

# Plot the number of hospitals with multiple reports over time
hospitals_over_time <- duplicate.hcris %>%
  group_by(fyear) %>%
  summarise(num_hospitals = n())

ggplot(hospitals_over_time, aes(x = fyear, y = num_hospitals)) +
  geom_line() +
  labs(x = "Fiscal Year", y = "Number of Hospitals with Multiple Reports") +
  ggtitle("Hospitals with Multiple Reports in the Same Year")

```

\newpage
#Question 2
```{r results="hide", echo=FALSE, message=FALSE}
num_unique_hospitals <- final.hcris.data %>%
  distinct(provider_number) %>%
  nrow()
```
The number of unique hospital IDs: 21886.

\newpage
#Question 3
```{r results="hide", echo=FALSE, message=FALSE}
library(ggplot2)
# Plot violin plot
ggplot(final.hcris.data, aes(x = as.factor(year), y = tot_charges)) +
  geom_violin() +
  labs(x = "Year", y = "Total Charges") +
  ggtitle("Distribution of Total Charges by Year")
```

\newpage
#Question 4
```{r results="hide", echo=FALSE, message=FALSE}
# Load necessary libraries
library(tidyverse)

# Load the HCRIS data
final.hcris.data <- read_rds("/Users/moyosoreoluwaodugbemi/Econ 470/Homework2/data/output/HCRIS_Data.rds")

# Calculate the estimated prices
final.hcris.data <- final.hcris.data %>%
  mutate(
    discount_factor = 1 - tot_discounts / tot_charges,
    price_num = (ip_charges + icu_charges + ancillary_charges) * discount_factor - tot_mcare_payment,
    price_denom = tot_discharges - mcare_discharges,
    price = price_num / price_denom
  )

# Filter out negative prices and extreme outliers
final.hcris.data <- final.hcris.data %>%
  filter(price >= 0) %>%
  filter(between(price, quantile(price, 0.01), quantile(price, 0.99)))  # Remove extreme outliers

# Create violin plot
ggplot(final.hcris.data, aes(x = as.factor(year), y = price)) +
  geom_violin(trim = FALSE) +
  labs(x = "Year", y = "Estimated Price") +
  ggtitle("Distribution of Estimated Prices by Year") +
  theme_minimal()
```

\newpage
#Question 5
```{r results="asis", echo=FALSE, message=FALSE}
# Filter the dataset to include only observations from the year 2012
data_2012 <- final.hcris.data %>% filter(year == 2012)

# Define penalty as whether the sum of the HRRP and HVBP amounts are negative
data_2012 <- data_2012 %>% 
  mutate(penalty = ifelse(hrrp_payment + hvbp_payment < 0, "Penalized", "Non-Penalized"))

# Calculate the average price for penalized hospitals and non-penalized hospitals separately
average_price <- data_2012 %>%
  group_by(penalty) %>%
  summarise(average_price = mean(price, na.rm = TRUE))

# Print the results
print(average_price)
```

\newpage
#Question 6
```{r results="asis", echo=FALSE, message=FALSE}
# Calculate quartiles based on bed size
quartiles <- quantile(final.hcris.data$beds, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = TRUE)

# Create indicator variables for quartiles
final.hcris.data <- final.hcris.data %>%
  mutate(quartile_1 = ifelse(beds <= quartiles[2], 1, 0),
         quartile_2 = ifelse(beds > quartiles[2] & beds <= quartiles[3], 1, 0),
         quartile_3 = ifelse(beds > quartiles[3] & beds <= quartiles[4], 1, 0),
         quartile_4 = ifelse(beds > quartiles[4], 1, 0))

# Calculate the average price among treated/control groups for each quartile
average_price_quartiles <- final.hcris.data %>%
  group_by(quartile_1, quartile_2, quartile_3, quartile_4) %>%
  summarise(average_price = mean(price, na.rm = TRUE))

# Print the table of the average price among treated/control groups for each quartile
print(average_price_quartiles)
```

Not sure what is going on with tibble

\newpage
#Question 7
```{r results="hide", echo=FALSE, message=FALSE}

```

Tried using the code from the slides. Still working on debugging the errors.


#Question 8
```{r results="hide", echo=FALSE, message=FALSE}

```

I would guess that they would be similar for the treatment effect to be valid. 

#Question 9
```{r results="hide", echo=FALSE, message=FALSE}

```


#Question 10
```{r results="hide", echo=FALSE, message=FALSE}

```

Learning new packages to install for matching. Running the R-code for some reason doesn't diplay the graphs until I preview the qmd.