---
title: "Homework2 Submission3"
author: "Moyo Odugbemi"
subtitle: "https://github.com/modugbe/homework2"
format: 
   pdf: 
     df-print: default
     output-file: "odugbemi-m-hwk2-3"
     output-ext: "pdf"
     header-includes:
        - \usepackage{float}
        - \floatplacement{table}{H}
---

```{r results="hide", echo=FALSE, message=FALSE}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```



```{r results="hide", echo=FALSE, message=FALSE}
#| include: false
#| eval: true
 
load("/Users/moyosoreoluwaodugbemi/Econ 470/Homework2/submission3/results/Hw2_workspace.Rdata")
```


\newpage
# Question 1 
Hospitals that filed more than one report in the same year is plotted.
The data is first combined and then the unique duplicates are filtered out for this graph. 
```{r results="hide", message=FALSE}
#| echo: false
#| label: hospitals-duplicate
#| fig-cap: "Hospitals with duplicate reports"

plot_hospitals_over_time
```

\newpage


# Question 2 
```{r results="asis", echo=FALSE, message=FALSE}
cat("The number of unique hospital IDs:", num_unique_hospitals, ".")
```

\newpage
# Question 3
```{r results="hide", message=FALSE, warning=FALSE}
#| echo: false
#| label: question-3
#| fig-cap: "Distribution of total charges in each year"

question3_plot
```

\newpage
# Question 4
```{r results="hide", message=FALSE}
#| echo: false
#| label: question-4
#| fig-cap: "Distribution of estimated prices in each year"

question4_plot
```

\newpage
# Question 5
```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
#| echo: false
#| label: tbl-avg-price
#| tbl-cap: "Average Price by Penalty"

options(knitr.kable.NA = 0)
knitr::kable(average_price,format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down")) 
```

\newpage
# Question 6
```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
#| echo: false
#| label: tbl-avg-price-quartile
#| tbl-cap: "Average Price by Quartile"

options(knitr.kable.NA = 0)
knitr::kable(average_price_by_quartile,format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down")) 
```



\newpage
# Question 7 
```{r echo=FALSE, message=FALSE, warning=FALSE}
#| echo: false
#| label: tbl-estimates
#| tbl-cap: "Average Effect Estimates Using different estimators"

options(knitr.kable.NA = 0)
knitr::kable(estimand_table,format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down")) 
```


\newpage
# Question 8
The treatment effects are identical for the 4 estimators.  

\newpage
# Question 9 
I don't think this is a causal effect of the penalty because it is estimated based on beds only and other variables are not controlled for. Matching with beds doesn't make penalized hospitals sufficiently similar to non-penalized ones in my opinion. Other things like location of the hospital, type of hospital (for-profit/non-profit), size, etc. should be controlled for. 

\newpage
# Question 10
Learning new packages to install for matching (update: this package is the one that messes with the select function). Running the R-code for some reason doesn't diplay the graphs until I preview the qmd. I learned how to make this work by calling specific parts of the result.